### 2025-10-20 Proposals/2025-NSF-EntropicGeometry/NarrativeBody.tex
Tasks for student

>>>>

Depending on the interests and skill of the graduate student, there are different ways to contribute. One possibility is to analyze what constructions and theorem from topological vector spaces can be generalized to topological convex spaces. This will help us better understand the relationship between the two, and possibly give insights in what properties the entropic structure may impose to bridge the gap. Another possibility is to see what results from classical and quantum information theory can be generalized to the entropic structure alone. Yet another possibility, since the JSD is the square of a distance function, finding sufficient conditions for a pseudo-distance to be the square of a distance my clarify what properties the entropic structure may impose.
